---
title: "multinets: Multilevel Network Analysis"
output: github_document
---
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Build Status](https://travis-ci.org/neylsoncrepalde/multinets.svg?branch=master)](https://travis-ci.org/neylsoncrepalde/multinets)
 
---
 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.2-6666ff.svg)](https://cran.r-project.org/)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/multinets)](https://cran.r-project.org/package=multinets)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange.svg?style=flat-square)](commits/master)
 
---
 
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->


`multinets` is an R package that provides tools to visualize and analyze Multilevel Network Data. It was built as an extension to the [`igraph`](http://igraph.org/r/) package.

## Installation

The `multinets` package is developed under control version using Git 
and is hosted in GitHub. You can download it from GitHub using `devtools`:
```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("neylsoncrepalde/multinets")
```


## Usage

As a basic example, we will plot a multilevel network. We are going to use `linked_sim`, a simulated multilevel network dataset.

```{r example, fig.width=8, fig.height=7}
library(igraph)
library(multinets)

# Load the dataset
data("linked_sim")

# Test if the data is a multilevel network
is_multilevel(linked_sim)

# Set the layout coordinates
l <- layout_multilevel(linked_sim, layout = layout_with_kk)

# Set different colors and shapes for each level vertices
linked_sim <- set_color_multilevel(linked_sim)
linked_sim <- set_shape_multilevel(linked_sim)

# Plot
plot(linked_sim, layout = l, vertex.size = 5, vertex.label = NA)
```
