---
title: "multinets: Multilevel Network Analysis"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

`multinets` is an R package that provides tools to visualize and analyze Multilevel Network Data. It was built as an extension to the [`igraph`](http://igraph.org/r/) package.

## Installation

The `multinets` package is developed under control version using Git 
and is hosted in GitHub. You can download it from GitHub using `devtools`:
```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("neylsoncrepalde/multinets")
```


## Usage

As a basic example, we will plot a multilevel network. We are going to use `linked_sim`, a simulated multilevel network dataset.

```{r example, fig.width=8, fig.height=7}
library(multinets)
data("linked_sim")

# Test if the data is a multilevel network
is_multilevel(linked_sim)

# Set the layout coordinates
l <- layout_multilevel(linked_sim, layout = layout_with_kk)

# Set different colors and shapes for each level vertices
linked_sim <- set_color_multilevel(linked_sim)
linked_sim <- set_shape_multilevel(linked_sim)

# Plot
plot(linked_sim, layout = l, vertex.size = 5, vertex.label = NA)
```
